Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-12-02 journal/ms.Rmd
remarks by george

 Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions. Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.  One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words. Another view suggests that learning is driven  by highly connected words in the external learning environment, instead of highly connected words in the early internal lexicon. The present study tests both scenarios systematically in both the phonological and semantic domains across 10 languages. We show that external connectivity in the learning environment drives growth in both production- and comprehension-based vocabularies, even controlling for word frequency and length. This pattern of findings suggests a word learning mechanism where children harness their statistical learning abilities to detect and learn highly connected words in the learning environment.

@@

```{r growth, fig.cap = "Illustration of the two growth scenarios. Filled grey circles represent known words (Internal) at a certain point in time. The empty, numbered circles represent words that have not yet been learned (External) and which are candidates to enter the lexicon next. The identity of the word that is going to be learned depends on the growth scenario.  Here the squares indicate the node that drives growth in each scenario and the hand pointer indicates which word is likely to be learned. For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to INT, the node 1 is more likely to enter the lexicon. For EXT, the utility of a candidate node is its degree in the entire network. According to EXT, the node 2 is more likely to enter the lexicon next.", fig.align = "center", out.width = "300px"}
knitr::include_graphics("figs/growth3.png")
```

@@

Finally, we use developmental data in 10 languages. Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains [@youn2016; @arbesman2010]. Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the way in which the children's networks grow. Thus, Cross-linguistic comparison is crucial to test what growth mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014]. 
 <!--
\footnote{The difference is more obvious in the phonological case where the network structure––and the distribution of word connectivity––can a priori change from language to language depending on various languistic conventions.}
-->

@@

We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist. Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94]. When filling out a CDI form, caregivers are either invited to indicate whether their child "understands" (comprehension) or "understands and says" (production) each of about 400-700 words. For younger children (e.g., 8 to 18 months in the English data), both comprehension and production are queried, whereas for older children (16 to 36 months) only production is queried. Due to these limitations, we use data from younger children to test comprehension and data from older children to test production. Following previous studies [@storkel2009; @hills2009], we restrict our analysis to nouns. Table \@ref(tab:stats) gives an overview of the data we used.

@@

We constructed semantic networks for English data following the procedure outlined in @hills2009, as follows. We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998]. This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target). For example, when given the word "ball", they might answer with the word "game". A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms. The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target. To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.

@@

In previous studies, two nodes were linked if they had an edit distance of 1 [@storkel2009; @carlson2014; @stella2017]. However, these studies reported a contribution of phonological connectivity to word learning when networks were built using a rich adult vocabulary. Since the focus of the current study is on the mechanism of growth, the networks should be based on the children's early vocabulary. The latter, nevertheless, contains very few word pairs with an edit distance of 1. Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold. In both cases, the results were weaker that those obtained with a threshold of 2.} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.

@@

Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \@ref(fig:growth)). Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition. This correlation is also compatible with INT, although the causality is reversed: higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time. Thus, the correlation between connectivity in the end-state network and AoA can result from both EXT and INT. If there is no such correlation, neither growth scenarios can be posited as a possible learning mechanism.

@@

Overall, we could not reject the null hypothesis of a power-law distribution: The $p$-value was generally above 0.1 in almost all languages for both production and comprehension. That said, phonological networks had relatively larger cut-offs than semantic networks. As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks –as well as the cross-linguistic variability in the value of the cut-offs– may reflect the various constraints that exist on word formation such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words. Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law.

@@

First, the results replicate Hills et al.'s original finding regarding the semantic network in English and the production-based vocabulary, which is that this network grows by EXT, not by INT. Second, our results show that, generally speaking, this finding generalizes to comprehension-based vocabulary, and holds across languages. This generalization was obtained in both the semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption, rather it supports our initial approximation about the universality of the semantic similarity measure.} and phonological domains.

>>>>

 Children tend to produce words earlier when they are connected to a variety of other words along the phonological and semantic dimensions. Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.  One view suggests that learning is primarily predicted by a network growth model where highly connected words in the child's early lexicon enable learning of similar words. Another view suggests that learning is driven  by highly connected words in the external learning environment, instead of highly connected words in the early internal lexicon. The present study tests both scenarios systematically in both the phonological and semantic domains across 10 languages. We show that external connectivity in the learning environment drives growth in both production- and comprehension-based vocabularies, even controlling for word frequency and length. This pattern of findings suggests a word learning mechanism where children harness their statistical learning abilities to detect and learn highly connected words in the learning environment.

@@

```{r growth, fig.cap = "Illustration of the two growth scenarios. Filled grey circles represent known words (Internal) at a certain point in time. The empty, numbered circles represent words that have not yet been learned (External) and which are candidates to enter the lexicon next. The identity of the word that is going to be learned depends on the growth scenario.  Here the squares indicate the node that drives growth in each scenario and the hand pointer indicates which word is likely to be learned. For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to INT, node 1 is more likely to enter the lexicon. For EXT, the utility of a candidate node is its degree in the entire network. According to EXT, node 2 is more likely to enter the lexicon next.", fig.align = "center", out.width = "300px"}
knitr::include_graphics("figs/growth3.png")
```

@@

Finally, we use developmental data in 10 languages. Lexical networks can show more or less cross-linguistic variability along both the semantic and phonological domains [@youn2016; @arbesman2010]. Besides, cultures might differ in the way caregivers talk to children [@kuhl1997; @cristia2017], and this difference in the input could influence the way in which the children's networks grow. Thus, cross-linguistic comparison is crucial to test what growth mechanism is cognitively universal and is used by all children, and what mechanism is specific to some patterns of learning that emerge due to the particulars of a given language or culture [@bates1987; @slobin2014]. 
 <!--
\footnote{The difference is more obvious in the phonological case where the network structure––and the distribution of word connectivity––can a priori change from language to language depending on various languistic conventions.}
-->

@@

We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist. Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94]. When filling out a CDI form, caregivers are either invited to indicate whether their child "understands" (comprehension) or "understands and says" (production) each of about 400-700 words. For younger children (e.g., 8 to 18 months in the English data), both comprehension and production are queried, whereas for older children (16 to 36 months) only production is queried. Due to these limitations, we use data from younger children to test comprehension and data from older children to test production. Following previous studies [@storkel2009; @hills2009], we restrict our analysis to the category of nouns.\footnote{This choice was also forced by the fact that the great majority of association data produced by adults–and which we used to build semantic networks–were nouns.}. Table \@ref(tab:stats) gives an overview of the data we used.

@@

We constructed semantic networks for English data following the procedure outlined in @hills2009, as follows. We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998]. This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target). For example, when given the word "ball", they might answer with the word "game". A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms. The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target.\footnote{This choice was based the prior work by @hills2009 stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated for indegree.} To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.

@@

In previous studies, two nodes were linked if they had an edit distance of 1 [@storkel2009; @carlson2014; @stella2017]. However, these studies reported a contribution of phonological connectivity to word learning when networks were built using a rich adult vocabulary. Since the focus of the current study is on the mechanism of growth, the networks should be based on children's early vocabulary. The latter, however, contains very few word pairs with an edit distance of 1. Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold. In both cases, the results were weaker than those obtained with a threshold of 2. We did not consider the case of a threshold larger than 2 since the pairs will become less and less phonologically related.} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.

@@

Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \@ref(fig:growth)). Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition. This correlation is also necessary to INT, although the causality is reversed: higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time. Thus, the correlation between connectivity in the end-state network and AoA can result from both EXT and INT. If there is no such correlation, neither growth scenario can be posited as a possible learning mechanism.

@@

Overall, we could not reject the null hypothesis of a power-law distribution: The $p$-value was generally above 0.1 in almost all languages for both production and comprehension. That said, phonological networks had relatively larger cut-offs than semantic networks. As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks may reflect the various constraints that exist on word formation in the phonological domain such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words. Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law.

@@

First, the results replicate Hills et al.'s original finding regarding the semantic network in English and the production-based vocabulary, which is that this network grows by EXT, not by INT. Second, our results show that, generally speaking, this finding generalizes to comprehension-based vocabulary, and holds across languages. This generalization was obtained in both the semantic^[One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption, rather it supports our initial approximation about the universality of the semantic similarity measure. That said, this apprimation is not perfect; for example there is evidence that a small part of the variance in free assication data can be explained by phonological similarity [@kachergis2011; @matusevych2018], thus leading to possibly minor cross-linguistic differences.] and phonological domains.

### 2018-12-02 journal/ms.tex
remarks by george

  \abstract{Children tend to produce words earlier when they are connected to a
variety of other words along both the phonological and semantic
dimensions. Though this connectivity effect has been extensively
documented, little is known about the underlying developmental
mechanism. One view suggests that learning is primarily driven by a
network growth model where highly connected words in the child's early
lexicon attract similar words. Another view suggests that learning is
driven by highly connected words in the external learning environment,
instead of highly connected words in the early internal lexicon. The
present study tests both scenarios systematically in both the
phonological and semantic domains across 10 languages. We show that
external connectivity in the learning environment drives growth in both
production- and comprehension-based vocabularies, even controlling for
word frequency and length. This pattern of findings suggests a word
learning mechanism where children harness their statistical learning
abilities to detect and learn highly connected words in the learning
environment.}
  \keywords{Language understanding; audio-visual processing; word learning; speech
perception; computational modeling. \\

@@

\caption{Illustration of the two growth scenarios. Filled grey circles represent known words (Internal) at a certain point in time. The empty, numbered circles represent words that have not yet been learned (External) and which are candidates to enter the lexicon next. The identity of the word that is going to be learned depends on the growth scenario.  Here the squares indicate the node that drives growth in each scenario and the hand pointer indicates which word is likely to be learned. For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to INT, the node 1 is more likely to enter the lexicon. For EXT, the utility of a candidate node is its degree in the entire network. According to EXT, the node 2 is more likely to enter the lexicon next.}\label{fig:growth}
\end{figure}

@@

Finally, we use developmental data in 10 languages. Lexical networks can
show more or less cross-linguistic variability along both the semantic
and phonological domains (Arbesman, Strogatz, \& Vitevitch, 2010; Youn
et al., 2016). Besides, cultures might differ in the way caregivers talk
to children (Cristia, Dupoux, Gurven, \& Stieglitz, 2017; Kuhl et al.,
1997), and this difference in the input could influence the way in which
the children's networks grow. Thus, Cross-linguistic comparison is
crucial to test what growth mechanism is cognitively universal and is
used by all children, and what mechanism is specific to some patterns of
learning that emerge due to the particulars of a given language or
culture (Bates \& MacWhinney, 1987; Slobin, 2014).

@@

We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
2017), an open repository aggregating cross-linguistic language
developmental data of the MacArthur-Bates Communicative Development
Inventory (CDI), a parent report vocabulary checklist. Parent report is
a reliable and valid measure of children's vocabulary that allows for
the cost-effective collection of datasets large enough to test
network-based models of acquisition (Fenson et al., 1994). When filling
out a CDI form, caregivers are either invited to indicate whether their
child \enquote{understands} (comprehension) or \enquote{understands and
says} (production) each of about 400-700 words. For younger children
(e.g., 8 to 18 months in the English data), both comprehension and
production are queried, whereas for older children (16 to 36 months)
only production is queried. Due to these limitations, we use data from
younger children to test comprehension and data from older children to
test production. Following previous studies (Hills et al., 2009;
Storkel, 2009), we restrict our analysis to nouns. Table \ref{tab:stats}
gives an overview of the data we used.

@@

We constructed semantic networks for English data following the
procedure outlined in Hills et al. (2009), as follows. We used as an
index of semantic relatedness the Florida Free Association Norms (Nelson
et al., 1998). This dataset was collected by giving adult participants a
word (the cue), and asking them to write the first word that comes to
mind (the target). For example, when given the word \enquote{ball}, they
might answer with the word \enquote{game}. A pair of nodes were
connected by a directed link from the cue to the target if there was a
cue-target relationship between these nodes in the association norms.
The connectivity of a given node was characterized by its
\emph{indegree}: the number of links for which the word was the target.
To model growth from month to month, we constructed a different network
at each month, based on the words that have been acquired by that month.

@@

In previous studies, two nodes were linked if they had an edit distance
of 1 (Carlson et al., 2014; Stella et al., 2017; Storkel, 2009).
However, these studies reported a contribution of phonological
connectivity to word learning when networks were built using a rich
adult vocabulary. Since the focus of the current study is on the
mechanism of growth, the networks should be based on the children's
early vocabulary. The latter, nevertheless, contains very few word pairs
with an edit distance of 1. Thus, we increased the threshold from 1 to
2, that is, two nodes were related if their edit distance was equal to 1
or
2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold. In both cases, the results were weaker that those obtained with a threshold of 2.}
The connectivity of a given node was characterized with its
\emph{degree}: the number of links it shares with other words.

@@

Connectivity in the global network is directly related to EXT as it
represents the explicit criterion this growth scenario uses to determine
what words should be learned first (Figure \ref{fig:growth}). Therefore,
a direct consequence of an EXT-like growth scenario is a correlation
between connectivity in the global network and the age of acquisition.
This correlation is also compatible with INT, although the causality is
reversed: higher connectivity in the global network is caused by earlier
learning, not the other way around. Some words end up being highly
connected in the global network precisely because they happen to be
acquired earlier and, therefore, have a higher chance of accumulating
more links over time. Thus, the correlation between connectivity in the
end-state network and AoA can result from both EXT and INT. If there is
no such correlation, neither growth scenarios can be posited as a
possible learning mechanism.

@@

Overall, we could not reject the null hypothesis of a power-law
distribution: The \(p\)-value was generally above 0.1 in almost all
languages for both production and comprehension. That said, phonological
networks had relatively larger cut-offs than semantic networks. As was
suggested by Arbesman et al. (2010), these \enquote{truncated}
power-laws in phonological networks --as well as the cross-linguistic
variability in the value of the cut-offs-- may reflect the various
constraints that exist on word formation such as the number of phonemes
in the language, the phonotactics (i.e., the way sound sequences are
arranged in words), and the length of words. Such constraints may limit
the number of words that are phonologically similar, thus leading to
distributions which decay faster than a non-truncated power law.

@@

First, the results replicate Hills et al.'s original finding regarding
the semantic network in English and the production-based vocabulary,
which is that this network grows by EXT, not by INT. Second, our results
show that, generally speaking, this finding generalizes to
comprehension-based vocabulary, and holds across languages. This
generalization was obtained in both the
semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption, rather it supports our initial approximation about the universality of the semantic similarity measure.}
and phonological domains.

@@

@@

>>>>

  \abstract{Children tend to produce words earlier when they are connected to a
variety of other words along the phonological and semantic dimensions.
Though this connectivity effect has been extensively documented, little
is known about the underlying developmental mechanism. One view suggests
that learning is primarily predicted by a network growth model where
highly connected words in the child's early lexicon enable learning of
similar words. Another view suggests that learning is driven by highly
connected words in the external learning environment, instead of highly
connected words in the early internal lexicon. The present study tests
both scenarios systematically in both the phonological and semantic
domains across 10 languages. We show that external connectivity in the
learning environment drives growth in both production- and
comprehension-based vocabularies, even controlling for word frequency
and length. This pattern of findings suggests a word learning mechanism
where children harness their statistical learning abilities to detect
and learn highly connected words in the learning environment.}
  \keywords{Language understanding; audio-visual processing; word learning; speech
perception; computational modeling. \\

@@

\caption{Illustration of the two growth scenarios. Filled grey circles represent known words (Internal) at a certain point in time. The empty, numbered circles represent words that have not yet been learned (External) and which are candidates to enter the lexicon next. The identity of the word that is going to be learned depends on the growth scenario.  Here the squares indicate the node that drives growth in each scenario and the hand pointer indicates which word is likely to be learned. For INT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to INT, node 1 is more likely to enter the lexicon. For EXT, the utility of a candidate node is its degree in the entire network. According to EXT, node 2 is more likely to enter the lexicon next.}\label{fig:growth}
\end{figure}

@@

Finally, we use developmental data in 10 languages. Lexical networks can
show more or less cross-linguistic variability along both the semantic
and phonological domains (Arbesman, Strogatz, \& Vitevitch, 2010; Youn
et al., 2016). Besides, cultures might differ in the way caregivers talk
to children (Cristia, Dupoux, Gurven, \& Stieglitz, 2017; Kuhl et al.,
1997), and this difference in the input could influence the way in which
the children's networks grow. Thus, cross-linguistic comparison is
crucial to test what growth mechanism is cognitively universal and is
used by all children, and what mechanism is specific to some patterns of
learning that emerge due to the particulars of a given language or
culture (Bates \& MacWhinney, 1987; Slobin, 2014).

@@

We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
2017), an open repository aggregating cross-linguistic language
developmental data of the MacArthur-Bates Communicative Development
Inventory (CDI), a parent report vocabulary checklist. Parent report is
a reliable and valid measure of children's vocabulary that allows for
the cost-effective collection of datasets large enough to test
network-based models of acquisition (Fenson et al., 1994). When filling
out a CDI form, caregivers are either invited to indicate whether their
child \enquote{understands} (comprehension) or \enquote{understands and
says} (production) each of about 400-700 words. For younger children
(e.g., 8 to 18 months in the English data), both comprehension and
production are queried, whereas for older children (16 to 36 months)
only production is queried. Due to these limitations, we use data from
younger children to test comprehension and data from older children to
test production. Following previous studies (Hills et al., 2009;
Storkel, 2009), we restrict our analysis to the category of
nouns.\footnote{This choice was also forced by the fact that the great majority of association data produced by adults–and which we used to build semantic networks–were nouns.}.
Table \ref{tab:stats} gives an overview of the data we used.

@@

We constructed semantic networks for English data following the
procedure outlined in Hills et al. (2009), as follows. We used as an
index of semantic relatedness the Florida Free Association Norms (Nelson
et al., 1998). This dataset was collected by giving adult participants a
word (the cue), and asking them to write the first word that comes to
mind (the target). For example, when given the word \enquote{ball}, they
might answer with the word \enquote{game}. A pair of nodes were
connected by a directed link from the cue to the target if there was a
cue-target relationship between these nodes in the association norms.
The connectivity of a given node was characterized by its
\emph{indegree}: the number of links for which the word was the
target.\footnote{This choice was based the prior work by @hills2009 stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated for indegree.}
To model growth from month to month, we constructed a different network
at each month, based on the words that have been acquired by that month.

@@

In previous studies, two nodes were linked if they had an edit distance
of 1 (Carlson et al., 2014; Stella et al., 2017; Storkel, 2009).
However, these studies reported a contribution of phonological
connectivity to word learning when networks were built using a rich
adult vocabulary. Since the focus of the current study is on the
mechanism of growth, the networks should be based on children's early
vocabulary. The latter, however, contains very few word pairs with an
edit distance of 1. Thus, we increased the threshold from 1 to 2, that
is, two nodes were related if their edit distance was equal to 1 or
2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold. In both cases, the results were weaker than those obtained with a threshold of 2. We did not consider the case of a threshold larger than 2 since the pairs will become less and less phonologically related.}
The connectivity of a given node was characterized with its
\emph{degree}: the number of links it shares with other words.

@@

Connectivity in the global network is directly related to EXT as it
represents the explicit criterion this growth scenario uses to determine
what words should be learned first (Figure \ref{fig:growth}). Therefore,
a direct consequence of an EXT-like growth scenario is a correlation
between connectivity in the global network and the age of acquisition.
This correlation is also necessary to INT, although the causality is
reversed: higher connectivity in the global network is caused by earlier
learning, not the other way around. Some words end up being highly
connected in the global network precisely because they happen to be
acquired earlier and, therefore, have a higher chance of accumulating
more links over time. Thus, the correlation between connectivity in the
end-state network and AoA can result from both EXT and INT. If there is
no such correlation, neither growth scenario can be posited as a
possible learning mechanism.

@@

Overall, we could not reject the null hypothesis of a power-law
distribution: The \(p\)-value was generally above 0.1 in almost all
languages for both production and comprehension. That said, phonological
networks had relatively larger cut-offs than semantic networks. As was
suggested by Arbesman et al. (2010), these \enquote{truncated}
power-laws in phonological networks may reflect the various constraints
that exist on word formation in the phonological domain such as the
number of phonemes in the language, the phonotactics (i.e., the way
sound sequences are arranged in words), and the length of words. Such
constraints may limit the number of words that are phonologically
similar, thus leading to distributions which decay faster than a
non-truncated power law.

@@

First, the results replicate Hills et al.'s original finding regarding
the semantic network in English and the production-based vocabulary,
which is that this network grows by EXT, not by INT. Second, our results
show that, generally speaking, this finding generalizes to
comprehension-based vocabulary, and holds across languages. This
generalization was obtained in both the semantic\footnote{One could
  imagine that the fact of using English free association norms
  cross-linguistically would decrease the effect of non-English semantic
  networks because of possible cultural differences. However, our
  findings do not support this assumption, rather it supports our
  initial approximation about the universality of the semantic
  similarity measure. That said, this apprimation is not perfect; there
  is evidence that a small part of the variance in free assication data
  can be explained by phonological similarity (Kachergis, Cox, \& Jones,
  2011; Matusevych \& Stevenson, 2018), thus leading to possibly minor
  cross-linguistic differences.} and phonological domains.

@@

\hypertarget{ref-kachergis2011}{}
Kachergis, G., Cox, G. E., \& Jones, M. N. (2011). OrBEAGLE: Integrating
orthography into a holographic model of the lexicon. In
\emph{International conference on artificial neural networks} (pp.
307--314). Springer.

@@

\hypertarget{ref-matusevych2018}{}
Matusevych, Y., \& Stevenson, S. (2018). Analyzing and modeling free
word associations. In \emph{Proceedings of the 40th Annual Conference of
the Cognitive Science Society}.
